Type cones of $\b{g}$-vector fans

### 2019-02-12 thirdPaper/draft/typeConeAssociahedra.tex
a bit more on extricats - cannot compile, may have introduced errors

@@

\begin{remark}
For any~$T\in\ind(\tc)$, fix an extriangle~$T\infl 0\defl\susp T\overset{\eps_T}{\dashrightarrow}$, and extend those choices to the all of~$\tc$ by additivity.
As noticed in Lemma~\ref{lemma::shifts of extriangles}, for any morphism~$T\overset{f}{\to}T'$ in~$\tc$, there is a unique morphism~$\susp f\in\cat(\susp T,\susp T')$ such that~$f_\ast\eps_T=(\susp f)^\ast\eps_{T'}$, as illustrated below:
\[
\xy
(-12,6)*+{T}="0";
(0,6)*+{0}="2";
(12,6)*+{\susp T}="4";
(24,6)*+{}="6";
%
(-12,-6)*+{T'}="10";
(0,-6)*+{0}="12";
(12,-6)*+{\susp T'}="14";
(24,-6)*+{}="16";
%
{\ar "0";"2"};
{\ar "2";"4"};
{\ar@{-->}^{\eps_T} "4";"6"};
%
{\ar_{f} "0";"10"};
{\ar "2";"12"};
{\ar^{\susp f} "4";"14"};
%
{\ar "10";"12"};
{\ar "12";"14"};
{\ar@{-->}_{\eps_{T'}} "14";"16"};
\endxy
\]
which gives an equivalence of additive categories
\[
 \susp: \tc \to \susp\tc
\]
where~$\susp\tc$ is the full subcategory of~$\cat$ whose objects are of the form~$\susp T$, for some~$T\in\tc$.
\end{remark}

@@

%%
\subsubsection{Associative algebras}
\begin{example}[A gentle algebra]
 Consider the algebra~$\Lambda$ given the the path algebra of the quiver
 \[
  \begin{tikzcd}
   1 \arrow[r, "\alpha"] & 2\arrow[r, "\beta"] & 3\arrow[r, "\gamma"] & 4
  \end{tikzcd}
 \]
 modulo the relation~$\gamma\beta\alpha = 0$.  The Auslander--Reiten quiver of the extriangulated category~$K^{[-1, 0]}(\proj\Lambda)$ is depicted below.
 \[
 \hspace*{-1cm}
 {\tiny
  \begin{tikzcd}
    &&&& (0\to P_4)\arrow[ddr] && (P_2\to 0)\arrow[ddr] && \\
    && (0\to P_3)\arrow[dr] && (P_1\to 0)\arrow[dr] &&&& \\
    & (0\to P_2)\arrow[dr]\arrow[ur] && (P_1\to P_3)\arrow[uur]\arrow[ur]\arrow[dr] && (P_2\to P_4)\arrow[uur]\arrow[dr] && (P_3\to 0)\arrow[dr] & \\
    (0\to P_1) \arrow[ur] && (P_1\to P_2)\arrow[ur] && (P_2\to P_3)\arrow[ur]  && (P_3\to P_4)\arrow[ur] && (P_4\to 0)
  \end{tikzcd}
 }
 \]
 The Auslander--Reiten of the module category is obtained by taking the quotient by the ideal generated by the shifted projective modules.
 \[
 \hspace*{-1cm}
 {\footnotesize
  \begin{tikzcd}
    &&&& \begin{matrix} 4\\3\\2 \end{matrix}\arrow[ddr] && \\
    && \begin{matrix} 3\\2\\1 \end{matrix}\arrow[dr] &&&& \\
    & \begin{matrix} 2\\1 \end{matrix}\arrow[dr]\arrow[ur] && \begin{matrix} 3\\2 \end{matrix}\arrow[uur]\arrow[dr] && \begin{matrix} 4\\3 \end{matrix}\arrow[dr] & \\
    \begin{matrix} 1 \end{matrix} \arrow[ur] && \begin{matrix} 2 \end{matrix}\arrow[ur] && \begin{matrix} 3 \end{matrix}\arrow[ur] && \begin{matrix}4 \end{matrix}
  \end{tikzcd}
 }
 \]
 The conditions of Theorem~\ref{theo::brick-algebra-condition} are satisfied.

>>>>

\tikzlibrary{matrix,quotes,arrows.meta}

@@

\begin{remark}\label{remark::equivalence Sigma}
For any~$T\in\ind(\tc)$, fix an extriangle~$T\infl 0\defl\susp T\overset{\eps_T}{\dashrightarrow}$, and extend those choices to the all of~$\tc$ by additivity.
As noticed in Lemma~\ref{lemma::shifts of extriangles}, for any morphism~$T\overset{f}{\to}T'$ in~$\tc$, there is a unique morphism~$\susp f\in\cat(\susp T,\susp T')$ such that~$f_\ast\eps_T=(\susp f)^\ast\eps_{T'}$, as illustrated below:
\[
\xy
(-12,6)*+{T}="0";
(0,6)*+{0}="2";
(12,6)*+{\susp T}="4";
(24,6)*+{}="6";
%
(-12,-6)*+{T'}="10";
(0,-6)*+{0}="12";
(12,-6)*+{\susp T'}="14";
(24,-6)*+{}="16";
%
{\ar "0";"2"};
{\ar "2";"4"};
{\ar@{-->}^{\eps_T} "4";"6"};
%
{\ar_{f} "0";"10"};
{\ar "2";"12"};
{\ar^{\susp f} "4";"14"};
%
{\ar "10";"12"};
{\ar "12";"14"};
{\ar@{-->}_{\eps_{T'}} "14";"16"};
\endxy
\]
This gives an equivalence of additive categories
\[
 \susp: \tc \to \susp\tc
\]
where~$\susp\tc$ is the full subcategory of~$\cat$ whose objects are isomorphic to objects of the form~$\susp T$, for some~$T\in\tc$.
\end{remark}

\begin{lemma}\label{lemma:: mphs in T are inflations}
Every morphism in~$\tc$ is an inflation.
\end{lemma}

\begin{proof}
Let~$T_1 \overset{t}{\to} T_0$ be a morphism in~$\tc$.
Using the notation of Remark~\ref{remark::equivalence Sigma}, there is an extriangle~$T_1\infl 0\defl \susp T_1 \overset{\eps_{T_1}}{\dashrightarrow}$.
Consider the extriangle~$T_0\overset{g}{\infl} X \overset{h}{\defl} \susp T_1 \overset{t_\ast\eps_{T_1}}{\dashrightarrow}$.
By~\cite[Proposition 3.17]{NakaokaPalu}, there is a commutative diagram of extriangles
\[
\xy
(-7,7)*+{T_1}="2";
(7,7)*+{0}="4";
(21,7)*+{\susp T_1}="6";
(28,7)*+{}="8";
%
(-7,-7)*+{T_0}="12";
(7,-7)*+{X}="14";
(21,-7)*+{\susp T_1}="16";
(28,-7)*+{}="18";
%
(-7,-21)*+{X}="22";
(7,-21)*+{X}="24";
%
(-7,-28)*+{}="32";
(7,-28)*+{}="34";
%
{\ar@{>->} "2";"4"};
{\ar@{->>} "4";"6"};
{\ar@{-->}^{\eps_{T_1}} "6";"8"};
%
{\ar@{>->}_{t'} "2";"12"};
{\ar "4";"14"};
{\ar@{=} "6";"16"};
%
{\ar^{g} "12";"14"};
{\ar^{h} "14";"16"};
{\ar@{-->}^{t_\ast\aps_{T_1}} "16";"18"};
%
{\ar_{g} "12";"22"};
{\ar^{1} "14";"24"};
%
{\ar@{=} "22";"24"};
%
{\ar@{-->}^{h^\ast\eps_{T_1}} "22";"32"};
{\ar@{-->} "24";"34"};
%
{\ar@{}|\circlearrowright "2";"14"};
{\ar@{}|\circlearrowright "4";"16"};
{\ar@{}|\circlearrowright "12";"24"};
\endxy
\]
satisfying~$(t')_\ast\eps_{T_1}=t_\ast\eps_{T_1}$.
We thus have~$t'=t$.
\end{proof}

\begin{remark}
 It follows from the proof of Lemma~\ref{lemma:: mphs in T are inflations} that conditions (1), (2), (3) in Setting~\ref{setting::extricat} are equivalent to conditions (1), (2), (3'), where
\[
{\rm (3')} \ \ \ \cat = \tc\ast\susp\tc.
\]
\end{remark}

\begin{proof}[Proof of Proposition~\ref{prop::KRextricat}]

\end{proof}

\begin{corollary}
The objects in~$\susp\tc$ are precisely the injective objects in~$\cat$.
\end{corollary}

@@

%%
\subsubsection{Associative algebras}
\begin{example}[A gentle algebra]
 Consider the algebra~$\Lambda$ given the the path algebra of the quiver
 \[
  \begin{tikzcd}
   1 \arrow[r, "\alpha"] & 2\arrow[r, "\beta"] & 3\arrow[r, "\gamma"] & 4
  \end{tikzcd}
 \]
 modulo the relation~$\gamma\beta\alpha = 0$.  The Auslander--Reiten quiver of the extriangulated category~$K^{[-1, 0]}(\proj\Lambda)$ is depicted below.
 \[
 \hspace*{-1cm}
 {\tiny
  \begin{tikzcd}
    &&&& (0\to P_4)\arrow[ddr] && (P_2\to 0)\arrow[ddr] && \\
    && (0\to P_3)\arrow[dr] && (P_1\to 0)\arrow[dr] &&&& \\
    & (0\to P_2)\arrow[dr]\arrow[ur] && (P_1\to P_3)\arrow[uur]\arrow[ur]\arrow[dr] && (P_2\to P_4)\arrow[uur]\arrow[dr] && (P_3\to 0)\arrow[dr] & \\
    (0\to P_1) \arrow[ur] && (P_1\to P_2)\arrow[ur] && (P_2\to P_3)\arrow[ur]  && (P_3\to P_4)\arrow[ur] && (P_4\to 0)
  \end{tikzcd}
 }
 \]
 The Auslander--Reiten quiver of the module category is obtained by taking the quotient by the ideal generated by the shifted projective modules.
 \[
 \hspace*{-1cm}
 {\footnotesize
  \begin{tikzcd}
    &&&& \begin{matrix} 4\\3\\2 \end{matrix}\arrow[ddr] && \\
    && \begin{matrix} 3\\2\\1 \end{matrix}\arrow[dr] &&&& \\
    & \begin{matrix} 2\\1 \end{matrix}\arrow[dr]\arrow[ur] && \begin{matrix} 3\\2 \end{matrix}\arrow[uur]\arrow[dr] && \begin{matrix} 4\\3 \end{matrix}\arrow[dr] & \\
    \begin{matrix} 1 \end{matrix} \arrow[ur] && \begin{matrix} 2 \end{matrix}\arrow[ur] && \begin{matrix} 3 \end{matrix}\arrow[ur] && \begin{matrix}4 \end{matrix}
  \end{tikzcd}
 }
 \]
 The conditions of Theorem~\ref{theo::brick-algebra-condition} are satisfied.
